### 2017-07-26 Paper01_EnthalpyAndCrystallization.tex
Method - work on DSC, casting, and Sputter

\subsection{Master alloy}
The master alloy of \MgZnCa~ was produced using high-purity elements of Mg (99.85 wt\%), Zn (99.995 wt\%), and Ca (99.8 wt\%). The alloy was prepared by induction melting in boron nitride coated graphite crucibles, purged with Ar (99.997 vol.\% purity) five times, and protected with a circulating Ar atmosphere. Alloy homogeneity was ensured through heating and cooling through a cycle 700\degree C, 385\degree C, 650\degree C, 385\degree C, 650\degree C to a casting temperature of 500 \degree C and 450\degree C for for injection and gravity casting respectively. Bulk amorphous \MgZnCa~ plate with a thickness of $XX \mu m$ was produced by copper mold injection casting. The $25.4 mm$ diameter targets were prepared from a cylindrical copper mold gravity casting sectioned to thicknesses of $3.25 mm$.

\subsection{\acrshort{dc} magnetron sputtering}
Films were produced from an in-house \acrshort{dc} magnetron sputtering facility with Ar working gas (99.997 vol.\% purity). The power was $15W$, typical voltage of $290-350V$, nominal chamber temperature of 25 \degree C, pressure 1 bar, Ar flow 3.01 \gls{sccm}.

\subsection{\acrshort{dsc} characterization}
DSC

@@

XRD heated in 5 degree increments at 20 k/min. scans of xx over a range of 31 - 60 2 theta allows 20 minute scans.

>>>>

\subsection{Master alloy}
The master alloy of \MgZnCa~ was produced using high-purity elements of Mg (99.85 wt\%), Zn (99.995 wt\%), and Ca (99.8 wt\%). The alloy was prepared by induction melting in boron nitride coated graphite crucibles, purged with Ar (99.997 vol.\% purity) five times, and protected with a circulating Ar atmosphere. Alloy homogeneity was ensured through heating and cooling through a cycle of 700\degree C, 385\degree C, 650\degree C, 385\degree C, 650\degree C to a casting temperature of 500 \degree C and 450\degree C for for injection and gravity casting respectively. Bulk amorphous \MgZnCa~ rod of $2.5 mm$ diameter and plates of thickness of $XX \mu m$ was produced by copper mold injection casting. The $25.4 mm$ diameter targets were prepared from a cylindrical copper mold gravity casting sectioned to thicknesses of $3.25 mm$.

\subsection{\acrshort{dc} magnetron sputtering}
Films were produced from an in-house \acrshort{dc} magnetron sputtering facility with Ar working gas (99.997 vol.\% purity). The power was $15W$, typical voltage of $290-350V$, nominal chamber pressure 1 bar, temperature of 25 \degree C, Ar flow 3.01 \gls{sccm}. Depositions were onto Al substrates for a period of 35 minutes.

\subsection{\acrshort{dsc} characterization}
Isochronic DSC (204 F1 Phoenix, Netzsch, Selb, Germany) was carried out in aluminium crucibles under protective argon atmosphere. Scans were performed at heating rates of 5 to 100 K/min.

@@

The temperature was raised in 5 K increments at 20 K/min. scans of xx over a range of 31 - 60 2 theta allows 20 minute scans.
